Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-01-25 ThesisJP/Background/background.tex
Written discussion of paper 3.
Small add-on to the motivation section.
Writing. Still some sections unfinished in discussion part.

@@

@@

@@

\section{Field Simulations}

>>>>

Add sentence about siemens and supersonic imagine scanners.

@@

Key selling points of ultrasound imaging: cost, safety and real-time user interaction.

One sentence about speckle tracking.

@@

Capon beamforming\footnote{The name ''Capon beamformer'' is due to work by J. Capon \todo{add citation} on seismic arrays \todo{Move to background.}} or minimum variance beamforming.

@@

\section{Field simulations}

### 2014-01-25 ThesisJP/Introduction/introduction.tex
Writing. Still some sections unfinished in discussion part.

\section{Motivation}
A rapid development in computer game technology and accompanying programming languages have recently provided researchers with small personal super computers, comprised in a single graphics card (\nom{GPU}{Graphics Processing Unit}). The latest graphics cards\footnote{As of January 2014} from both \nom{Nvidia}{Graphics card producer} and \nom{AMD}{Graphics card producer} provides close to 6 T\nom{FLOPS}{Floating point operations per second} single precision and 1.5 TFLOPS double precision. For double precision this is more than the worlds most powerful supercomputer could provide in 1998.

This immense rise in computational power and programming flexibility gives new possibilities when designing ultrasound imaging systems. Algorithms which previously had to be implemented in hardware for performance reasons can now be implemented in software. And algorithms, either too complicated to implement in hardware, or though to be too computationally heavy for real-time use, becomes realizable. It is clear that high-performance programmable processors, like the GPU, already have and will continue to make future ultrasound imaging systems more flexible, cheaper to produce, and equipped with even more cutting-edge processing.

The Capon beamformer\footnote{The name ''Capon beamformer'' is due to work by J. Capon \todo{add citation} on seismic arrays \todo{Move to background.}}  is a good example of an algorithm which has been highly studied for the last decade for the application of medical ultrasound imaging \todo{cite papers}, but where the number of calculations was though to be too high for real-time processing to happen any time soon. No wonder, to achieve real-time processing for e.g. cardiac ultrasound imaging, an effective processing rate of around 100 MFLOPS is required. This number, as explained in Background \ref{sec:adaptbf}, also grows with larger subarrays, an increasing number of samples, and higher frame rates.  Nevertheless, with modern GPUs, these levels of processing are finally available in a single card. When researchers are exploring new algorithms for ultrasound imaging it is therefore important to keep the architecture of parallel accelerators in mind. If the algorithm is suppose to run in real time it needs to fit the programmable and parallel pipeline of modern ultrasound scanners.

@@

Well on my way into the project, when a real-time Capon beamformer was realized, and loops of images for the first time were processed, new issues where discovered and had to be solved. This led me to a more theoretical study of the Capon beamformer (\textbf{Paper III}), with special attention on how to obtain high lateral resolution while preserving the important shift-invariant property of medical ultrasound imaging. Shift-invariant behavior is crucial if the method is ever to be applied for live scanning.

@@

\subsection{Paper II}
\textbf{Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}\\
\textbf{J.\:P.\:\AA{}sen}, J.\:I.\:Buskenes, C.-I.\:C\:Nilsen, A.\:Austeng and S.\:Holm\\
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, no. 1, pp. \todo{add pages}, Jan. 2014.}\\\\
The second paper aims at achieving real-time Capon beamforming for cardiac ultrasound imaging. Such an implementation will facilitates further study of the method's \textit{in vivo} performance for this modality. This is something which has been sought for the past decade \todo{Add citations}. In \textbf{Paper I} we investigated arrays with no more than 32 elements. A linear array for cardiac ultrasound imaging typically has 64 or more elements. In \textbf{Paper VI}, which is summarized in \textbf{Paper II}, it is shown that our implementation from  \textbf{Paper I} does not reach the level of throughput required for real-time Capon beamforming of cardiac ultrasound imaging. The matrices that have to be inverted becomes to large, and the number of frames that needs to be processed per second is to many.

@@

\subsection{Paper III}
\textbf{Capon Beamforming and Moving Objects - An Analysis of Lateral Shift-Invariance}\\
\textbf{J.\:P.\:\AA{}sen}, A.\:Austeng and S.\:Holm\\
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, submitted.}\\\\
In the third paper we study the shift-invariant property of an imaging system based on the Capon beamformer. As mentioned, shift-invariant imaging is essential if the method is ever to be adopted. The paper was written based on observations of aliasing artifacts when imaging bright point scatterers \textit{in vitro} and in simulations. The points were observed to twinkle like stars in the sky. In earlier work on Capon beamforming for medical ultrasound imaging the real-time nature of ultrasound imaging has often been ignored, and a large degree of oversampling on transmit might have been applied without comments. Oversampling on transmit is not an option if the imaging modality is used to image rapidly varying objects. Smooth presentation of probe motion is also important in most ultrasound imaging applications. Real-time user interaction is one of the key selling points for ultrasound imaging.

@@

\subsection{Paper IV}
\textbf{Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}\\
\textbf{J.\:P.\:\AA{}sen}, E.\:Steen, G.\:Kiss, A.\:Thorstensen and S.\:I.\:Rabben\\
{\it Proc. SPIE Medical Imaging 2012, \todo{add pages}.}\\\\
The fourth paper propose an adaptive volume rendering method based on statistics derived from the blood pool of the left ventricle. Noise located in the blood pool tends to occlude cardiac tissue when rendered in 3D, and is often impossible to remove by adjusting global rendering parameters. This because ultrasound signals have high variability within blood as well as high variability within tissue, even when heavily smoothed. Delineated of the blood pool is done by a state estimation algorithm, capable of tracking the endocardium in real time. The final visualizations are compared, with respect to location of tissue, with the result from a state-of-the-art endocardium segmentation tool. The paper presents both quantitative and qualitative results supporting the method's improved capabilities of reducing tissue dropouts and spurious structures inside the blood pool, and by that maximizing the amount of visible endocardium tissue. The proposed method is implemented on a GPU which results in interactive frame rates.

\subsection{Paper V}
\textbf{Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}\\
\textbf{J.\:P.\:\AA{}sen} and S.\:Holm\\
{\it Proc. IEEE Ultrasonics Symposium 2012 \todo{add pages}.}\\\\
The fifth paper presents an interactive simulations tool capable of simulating dense pressure fields from ultrasound arrays in real time. Simulation tools are heavily used by researchers in order to test out new algorithms and to deduce the performance of new array designs prior to manufacturing. But dense simulations also involves a lot of calculations and waiting. With the presented simulator we try to reduce the time for calculating pressure fields by means of GPU acceleration. The tool is based on Huygens' principle which describes diffraction caused by a slit as the super position of several point sources located inside the opening. Thus, the simulator works by accumulating the contribution from a collection of point sources in a set of observation points. How the source and observation points are laid out is up to the user to decide. Points position along a line will for example simulate an ultrasound array. The simulator is linked with both a paint-like interface for interactive drawing of arrays, and a Matlab interface for precise scripting of array configurations. The main contributions in this paper is the increased performance of the GPU implementation compared with a CPU and Matlab\footnote{The Ultrasim toolbox \todo{add citation}} version. Second, the paint-like interface provides a neat way of demonstrating array beamforming principle in real time. We believe this to be of great value both for array designers and teachers.

\section{Main contributions}
The main contributions of this thesis are:
\begin{enumerate}
\item a GPU implementation of the Capon beamformer
\item a GPU implementation of the beamspace Capon beamformer
\item that real-time beamspace Capon beamforming is achieved for cardiac ultrasound imaging
\item the first investigation of Capon beamforming applied on multiple frames in medical ultrasound imaging (simulated, \textit{in vitro}, and \textit{in vivo})
\item an investigation of shift-invariance when using the Capon beamformer
\item a method for improved shift-invariance of the Capon beamformer
\item a method for reduced blood-pool noise in volume renderings of cardiac ultrasound volumes
\item a GPU implementation of this adaptive volume rendering method
\item a GPU implementation of simple paint-like simulation tool for rapid visualization ultrasound pressure fields
\end{enumerate}

In addition, the thesis provides several discussions on how to utilize the GPU to accelerate advanced ultrasound imaging algorithms.

@@

In \textbf{Paper II} we focused on achieving real time Capon processing for cardiac ultrasound by implementing the BS-Capon beamformer on a GPU. However, we also present the first medical ultrasound loops processed with ES- and BS-Capon beamforming.  The paper does not provide any detailed evaluation of the method's \textit{in vivo} performance. Yet, initially is has been proven hard to transfer results obtained in simulations to \textit{in vivo} images. The improvements seen are minimal, especially with the number of calculations in mind. The beamformers are clearly able to decrees the lateral width of lateral point scatterers and thin structures \textit{in vivo}, and to sharpen step edges. On the other hand, the overall contrast is visually not improved and sometimes it is worse (Fig.\,6b of \textbf{Paper II}). Since the Capon beamformer only affect directional noise, it is clear that contrast will get worse in low \nom{SNR}{Signal-to-noise ratio} applications when signal cancellation occurs. The oversampling approach presented in \textbf{Paper III} might improve on this, but it will only reduce signal cancellation if the phase shifts across the aperture are small and close to linear. Another issue is that bright points with a wide lateral profile exhibits better visual contrast when surrounded by speckle noise than points with narrow lateral profiles. In future work a detailed investigation of why some results obtained in simulations are not transferable to \textit{in vivo} needs to be performed. It will also be crucial to show larger improvements \textit{in vivio} than what is presented in \textbf{Paper II}. Both to justify all our computations, and to show an image which has both highly improved resolution and contrast. As pointed out at the end of \textbf{Paper II}, cardiac ultrasound might not be the best modality for Capon beamforming. Cardiac ultrasound imaging was selected because it is the medical ultrasound modality which requires most calculations per second. An application where the focus is detection of closely spaced point targets, might be better suited. A better suited adaptive beamformer for cardiac applications is the low-complexity beamformer (\nom{LCA}{Low complexity beamformer}) beamformer, where the Capon optimization problem is applied on a set of predefined windows. This method has linear complexity and shares many properties with the Capon beamformer. 

@@

In \textbf{Paper3} we investigate the inherent self nulling involved with Capon beamforming, and that this effect comes naturally into play when the beamformer is subjected to linear steering vector errors caused by lateral undersampling. These errors are naturally reduced when the lateral sampling is increased. This is something which has not been talked much about in the literature, either due to ignorance or its impact on imaging frame rate. It is not that strange since nobody have looked at Capon beamforming on multiple consecutive frames before, especially not for real time imaging. Fortunately, as shown in \textbf{Paper III}, it is possible to maintain the same frame rate as with DAS by applying oversampling on receive using a set of steering vectors. It also turns out that we don't need to perform more matrix inversions either. Oversampling on receive will of course increase the penalty of applying processing, like filtering,  on scan-grid data. Scan conversion from a polar to Cartesian display grid will also take more time, and the end result should also have high resolution in order to preserve the un-sharpening introduced by Capon beamforming. The oversampling method might help at improving contrast since the amount of signal cancellation is reduced. It will not correct for steering vector errors caused by phase aberrations. At best it will correct for the linear term introduced by the aberrator.
With improved shift-invariance it will be interesting to see if high resolution beamforming could act as a post-processing step for other algorithms. For example to increase the precision of speckle tracking. In the case where the image is generated for post processing it does not need to be visually pleasant anymore as long as we avoid signal cancellation. Good looking speckle, or DAS-like speckle, has been the driving force behind many of the robustification techniques seen in the literature.

@@

Paper4

Chicken-or-egg method. If the tracking fails we will fail. View-dependent visibility.

@@

Statistics derived from the selected window by e.g Capon beamforming or the LCA beamformer might be utilized to adjust the opacity. It can also be used as input to image filtering. A adaptive window will be symmetric in homogeneous regions and left-right shifted close to tissue interfaces. In that way we can apply less filtering and higher opacity on edges. If this will be different than just looking at neighboring pixels is to be seen.
\\\\
Paper5

This is not an adaptive algorithm.

Mark that code for GPU-Capon and Huygens on speed have been made open source.
It has over 200 downloads and soon 1000 views on youtube.

Integrated beamforming and visualization. Using adaptive beamforming to improve e.g. speckle tracking and segmentation. Use adaptive weight statistics to guide image smoothing.

\endinput

>>>>

\section{Motivation}
A rapid development in computer game technology and accompanying programming languages have recently provided researchers with small personal super computers, comprised in a single graphics card (\nom{GPU}{Graphics Processing Unit}). The latest graphics cards\footnote{As of January 2014.} from both \nom{Nvidia}{Graphics card producer} and \nom{AMD}{Graphics card producer} provide close to 6 T\nom{FLOPS}{Floating point operations per second} single precision and 1.5 TFLOPS double precision. For double precision this is more than the worlds most powerful supercomputer could provide in 1998.

This immense rise in computational power and improved programmability are changing how ultrasound imaging systems are designed. Algorithms which previously had to be implemented in hardware for performance reasons can now be implemented in software. And algorithms, either too complicated to implement in hardware, or though to be too computationally heavy for real-time use, becomes realizable. It is clear that high-performance programmable processors, like the GPU, already have and will continue to make future ultrasound imaging systems more flexible, cheaper to produce, and equipped with even more cutting-edge processing.

The Capon beamforme  is a good example of an algorithm which has been highly studied for the last decade for the application of medical ultrasound imaging, but where the number of calculations was though to be too high for real-time processing to happen any time soon. No wonder, to achieve real-time processing for e.g. cardiac ultrasound imaging, an effective processing rate of around 100 MFLOPS is required. This number, as explained in Background \ref{sec:adaptbf}, also grows with larger subarrays, an increasing number of samples, and higher frame rates.  Nevertheless, with modern GPUs, these levels of processing are finally available within a single card. When researchers are exploring new algorithms for ultrasound imaging it is therefore important to keep the architecture of parallel accelerators in mind. If the algorithm is suppose to run in real time it needs to fit the programmable and parallel pipeline of modern ultrasound scanners.

@@

Well on my way into the project, when a real-time Capon beamformer was realized, and loops of images for the first time were processed at interactive and real-time frame rates, new issues where discovered and had to be solved. This led me to a more theoretical study of the Capon beamformer (\textbf{Paper III}), with special attention on how to obtain high lateral resolution while preserving the important shift-invariant property of medical ultrasound imaging. Shift-invariant behavior is crucial if the method is ever to be applied for live scanning.

@@

\subsection{Paper II}
\textbf{Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}\\
\textbf{J.\:P.\:\AA{}sen}, J.\:I.\:Buskenes, C.-I.\:C\:Nilsen, A.\:Austeng and S.\:Holm\\
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. 61, no. 1, pp. \todo{add pages}, Jan. 2014.}\\\\
The second paper aims at achieving real-time Capon beamforming for cardiac ultrasound imaging. Such an implementation will facilitates further study of the method's \textit{in vivo} performance for this modality. This is something which has been sought for the past decade \todo{Add citations}. In \textbf{Paper I} we investigated arrays with no more than 32 elements. A linear array for cardiac ultrasound imaging typically has 64 or more elements. In \textbf{Paper VI}, which is summarized in \textbf{Paper II}, it is shown that our implementation from  \textbf{Paper I} does not reach the level of throughput required for real-time Capon beamforming of cardiac ultrasound imaging. The matrices that have to be inverted become to large, and the frames that needs to be processed per second are to many.

@@

\subsection{Paper III}
\textbf{Capon Beamforming and Moving Objects - An Analysis of Lateral Shift-Invariance}\\
\textbf{J.\:P.\:\AA{}sen}, A.\:Austeng and S.\:Holm\\
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, submitted.}\\\\
In the third paper we study the shift-invariant property of an imaging system based on the Capon beamformer. As mentioned, shift-invariant imaging is essential if the method is ever to be adopted. The paper was written based on observations of aliasing artifacts when imaging bright point scatterers \textit{in vitro} and in simulations. The points were observed to twinkle like stars in the sky. In earlier work on Capon beamforming for medical ultrasound imaging the real-time nature of ultrasound imaging has often been ignored, and a large degree of oversampling on transmit might have been applied without comments. Oversampling on transmit is not an option if the imaging modality is used to image rapidly varying objects. Smooth presentation of probe motion is also important in most ultrasound imaging applications. Real-time user interaction is one of the key selling points for ultrasound imaging and frame rate should therefore not be lower than 10 frames per second.

@@

\subsection{Paper IV}
\textbf{Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}\\
\textbf{J.\:P.\:\AA{}sen}, E.\:Steen, G.\:Kiss, A.\:Thorstensen and S.\:I.\:Rabben\\
{\it Proc. SPIE Medical Imaging 2012, \todo{add pages}.}\\\\
The fourth paper propose an adaptive volume rendering method based on statistics derived from the blood pool of the left ventricle. Noise located in the blood pool tends to occlude cardiac tissue when rendered in 3D, and is often impossible to remove by adjusting global rendering parameters. This because ultrasound signals have high variability within blood as well as high variability within tissue, even when heavily smoothed. Delineated of the blood pool is done by a state estimation algorithm, capable of tracking the endocardium in real time. The final visualizations are compared, with respect to location of tissue, with the result from a state-of-the-art endocardium segmentation tool. The paper presents both quantitative and qualitative results supporting the method's improved capabilities of reducing tissue dropouts and spurious structures inside the blood pool, and by that maximizing the amount of visible endocardium tissue. The proposed method is implemented on a GPU with interactive frame rates as the result.

\subsection{Paper V}
\textbf{Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}\\
\textbf{J.\:P.\:\AA{}sen} and S.\:Holm\\
{\it Proc. IEEE Ultrasonics Symposium 2012 \todo{add pages}.}\\\\
The fifth paper presents an interactive simulations tool capable of simulating dense pressure fields from ultrasound arrays in real time. Simulation tools are heavily used by researchers in order to test out new algorithms and to deduce the performance of new array designs prior to manufacturing. But dense simulations also involves a lot of calculations and waiting. With the presented simulator we try to reduce the time for calculating pressure fields by means of GPU acceleration. The tool is based on Huygens' principle which describes diffraction caused by a slit as the super position of several point sources located inside the opening. Thus, the simulator works by accumulating the contribution from a collection of point sources in a set of observation points. How the source and observation points are laid out is up to the user to decide. Point sources positioned along a line will for example simulate an ultrasound array. The simulator is linked with both a paint-like interface for interactive drawing of arrays, and a Matlab interface for precise scripting of array configurations. The main contributions in this paper is the increased performance of the GPU implementation compared with a CPU and Matlab\footnote{The Ultrasim toolbox \todo{add citation}} version. Second, the paint-like interface provides a neat way of demonstrating array beamforming principle in real time. We believe this to be of great value both for array designers and teachers.

\section{Main contributions}
The main contributions of this thesis are:
\begin{enumerate}
\item a GPU implementation of the Capon beamformer.
\item a GPU implementation of the beamspace Capon beamformer.
\item that real-time beamspace Capon beamforming is achieved for cardiac ultrasound imaging.
\item the first investigation of Capon beamforming applied on multiple frames in medical ultrasound imaging (simulated, \textit{in vitro}, and \textit{in vivo}).
\item an investigation of shift-invariance when the Capon beamformer is applied on consecutive frames.
\item a method for improved shift-invariance of the Capon beamformer.
\item a method for reduced blood-pool noise in volume renderings of cardiac ultrasound volumes.
\item a GPU implementation of this adaptive volume rendering method.
\item a GPU implementation of simple paint-like simulation tool for rapid visualization ultrasound pressure fields.
\end{enumerate}
In addition, the thesis provides several discussions on how to utilize the GPU to accelerate advanced ultrasound imaging algorithms.

@@

In \textbf{Paper II} we focused on achieving real time Capon processing for cardiac ultrasound by implementing the BS-Capon beamformer on a GPU. However, we also present the first medical ultrasound loops processed with ES- and BS-Capon beamforming.  The paper does not provide any detailed evaluation of the method's \textit{in vivo} performance. Yet, initially is has been proven hard to transfer all results obtained in simulations to \textit{in vivo} images. The improvements seen are minimal, especially with the number of calculations in mind. The beamformers are clearly able to decrees the lateral width of lateral point scatterers and thin structures \textit{in vivo}, and to sharpen step edges. On the other hand, the overall contrast is visually not improved and sometimes it is worse (Fig.\,6b of \textbf{Paper II}). Since the Capon beamformer only affect directional noise, it is clear that contrast will get worse in low \nom{SNR}{Signal-to-noise ratio} situations when signal cancellation occurs. The oversampling approach presented in \textbf{Paper III} might improve on this, but it will only reduce signal cancellation if the phase shifts across the aperture are close to linear and small. Another issue is that bright points with a wide lateral profile exhibits better visual contrast when surrounded by speckle noise than points with narrow lateral profiles. In future work a detailed investigation of why some results, especially the contrast, obtained in simulations are not transferable to \textit{in vivo} needs to be performed. It will also be crucial to show larger improvements \textit{in vivio} than what is presented in \textbf{Paper II}. Both to justify all our computations, and to show an image which has both highly improved resolution and contrast. As pointed out at the end of \textbf{Paper II}, cardiac ultrasound imaging might not be the best modality for Capon beamforming. Cardiac ultrasound imaging was selected because it is the medical ultrasound modality which requires most calculations per second. An application where the focus is detection of closely spaced point targets, might be better suited. A better suited adaptive beamformer for cardiac applications might be the low-complexity adaptive beamformer (\nom{LCA beamformer}{Low complexity adaptive beamformer}), where the Capon optimization problem is applied on a set of predefined windows. This method has linear complexity and shares many properties with the Capon beamformer. If only minor improvements are obtained, it would be easier to ignore this fact if the algorithm is less costly. Finally, it would also be interesting to see how the Eigenspace-based Capon beamformer performs on cardiac images, and how its absence of a distortionless criterion will influence the image spatially and temporally.

@@

In \textbf{Paper3} we investigate the inherent self nulling involved with Capon beamforming, and how this effect comes naturally into play when the beamformer is subjected to linear steering vector errors caused by lateral undersampling. These errors are naturally reduced when the lateral sampling is increased. This simple observation is something which has been missing in the literature on Capon beamforming for medical ultrasound imaging. The reason could be ignorance or its possible negative impact on imaging frame rate. A lack of studies where Capon beamforming is performed on consecutive frames might also explain its absence. Fortunately, as shown in \textbf{Paper III}, it is possible to maintain the same frame rate as with DAS beamforming by applying oversampling on receive using a set of steering vectors (phase delays). It turns out that we do not need to perform more matrix inversions either. Oversampling on receive will, however,  increase the penalty of applying post-processing, like filtering,  on scan-grid data. %The time taken to convert data from a polar scan grid to a Cartesian display grid will also increase. The Cartesian grid should also have high resolution in order to preserve the un-sharpening introduced by Capon beamforming. 
As just mentioned in the discussion of \textbf{Paper II}, the reduced signal cancellation should prevent contrast from degrade to less than the contrast obtain with DAS. It will, however,  not correct for signal cancellation caused by phase aberrations. At best it will correct for the linear term introduced by the aberrator if the term is small.
With improved shift-invariance it will also be interesting to see if high resolution beamforming could act as a post-processing step for other algorithms. For example to increase the precision of speckle and edge tracking. In the case where the image is generated for post processing it does not need to be visually pleasant anymore, as long as signal cancellation is avoided. Good looking speckle, or DAS-like speckle, has been the driving force behind many of the robustification techniques and the default parameters seen in the literature. Hence, more aggressive parameters might be used if the image produced is intended as input to another algorithm.

@@

Objections to \textbf{Paper IV} includes its inherent chicken-or-egg dilemma. The visualization is adjusted based on the data acquired by a user. The user sees the visualization and adjust scanning based on the visual input. This recursive behavior suggest that the method is best suited for post-processing when data has been recorded and saved.

It is also clear that if the tracking fails the suggested method will fail.

Does data need to be saved in order to perform tracking?

View-dependent visibility.

@@

Statistics derived from the selected window by e.g Capon beamforming or the LCA beamformer might be utilized to adjust the opacity. It can also be used as input to image filtering. A adaptive window will be symmetric in homogeneous regions and left-right shifted close to tissue interfaces. In that way we can apply less filtering and higher opacity on edges. If this will be different than just looking at neighboring pixels is to be seen.

Integrated beamforming and visualization. Using adaptive beamforming to improve e.g. speckle tracking and segmentation. Use adaptive weight statistics to guide image smoothing.
\\\\
The fifth paper stands out from the other papers by not dealing with an adaptive processing technique. It is still, however, centered around the topic of GPU implementation of algorithms for ultrasound imaging. Ultrasound simulations are typically used for research and to pre-calculate configurations of a given scan sequence. The continuously growth in computational power will, in the future, make it possible to evaluate a scan sequence on the fly, removing the need for

Achieving higher processing speed for an excising algorithm is not impressive as long as there is no novel analysis of the method modification    and the increase does not enables new ways of utilizing the increased speed.

The simulator has been download 200 times and have close to 1000 views on youtube.

Fast calculation of pressure fields can be used to automatically evaluate the pressure field of the current scan sequence. Hence, we can optimize weights etc. on the fly.
\\\\
The code for both the Capon beamformer and the ultrasound field simulator have been made open source and is available on github\footnote{github.com/jpaasen/hos and github.com/jpaasen/cos}. 
\endinput
